Describe Participants: Characteristics, Diet, and Cardiometabolic Risk

### 2022-03-24 Rmarkdown/analysis/Characteristics_Diet_CardiometabolicRisk_211111.Rmd
Limit to paper

1)

**Sources:**

@@

```{r Participant characterisitics by TMAO quantile}
# TMAO table by age bin - females
factorVars <- c("age_cat", "tmao_quantile")
vars <- c("age", "ethnicity" , "bmi_final", "waistavg_cm", "sysbpavgv2", "diabpavgv2", "endo_rhi", "endo_al", "hdl_bd1", "ldl_bd1", "chol_bd1", "tg_bd1", "glc_bd1", "insulin_bd1", "tnfa_bd1", "il6_bd1", "crp_bd1.mgdL", "cystatinc_bd1", "tmao", "choline", "betaine", "carnitine")
table_tmao.fq <- CreateTableOne(vars = vars,
                                    strata = "tmao_quantile",
                                    data = phen[phen$sex == "Female",],
                                    factorVars = factorVars)
table_tmao.fq

# TMAO table by age bin - males
factorVars <- c("age_cat", "tmao_quantile")
vars <- c("age", "ethnicity" , "bmi_final", "waistavg_cm", "sysbpavgv2", "diabpavgv2", "endo_rhi", "endo_al", "hdl_bd1", "ldl_bd1", "chol_bd1", "tg_bd1", "glc_bd1", "insulin_bd1", "tnfa_bd1", "il6_bd1", "crp_bd1.mgdL", "cystatinc_bd1", "tmao", "choline", "betaine", "carnitine")
table_tmao.mq <- CreateTableOne(vars = vars,
                                    strata = "tmao_quantile",
                                    data = phen[phen$sex == "Male",],
                                    factorVars = factorVars)
table_tmao.mq

# TMAO table by sex
factorVars <- c("tmao_quantile")
vars <- c("age", "ethnicity" , "bmi_final", "waistavg_cm", "sysbpavgv2", "diabpavgv2", "endo_rhi", "endo_al", "hdl_bd1", "ldl_bd1", "chol_bd1", "tg_bd1", "glc_bd1", "insulin_bd1", "tnfa_bd1", "il6_bd1", "crp_bd1.mgdL", "cystatinc_bd1", "tmao", "choline", "betaine", "carnitine")
table_tmao.allq <- CreateTableOne(vars = vars,
                                    strata = "tmao_quantile",
                                    data = phen,
                                    factorVars = factorVars)
table_tmao.allq
```

```{r Save characteristic quantile tables}
table_save.fq <- print(table_tmao.fq, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
write.csv(table_save.fq, file = "../../Outputs/tables/ParticipantChar/Characteristics_Female_byTMAOQuantile_211203.csv")

table_save.mq <- print(table_tmao.mq, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
write.csv(table_save.mq, file = "../../Outputs/tables/ParticipantChar/Characteristics_Male_byTMAOQuantile_211203.csv")

table_save.allq <- print(table_tmao.allq, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
write.csv(table_save.allq, file = "../../Outputs/tables/ParticipantChar/Characteristics_All_byTMAOQuantile_211203.csv")
```

Make similar tables but for TMAO tertile

@@

Save
```{r save food linear regression table}
# Save table
write.csv(res_food, "../../Outputs/tables/Diet/MultipleLinReg_TMAO_LCMS_n356_ASA24.csv")
```

Make TMAO food intake by quantile table
```{r Food Intake by TMAO quantile}
# TMAO table by age bin - females
factorVars <- c("age_cat", "tmao_quantile")
vars <- c("pf_meat_totals", 
          "pf_curedmeat_totals",
          "pf_poult_totals",
          "pf_seafd_hi_totals",
          "pf_seafd_low_totals",
          "pf_eggs_totals",
          "pf_nutsds_totals",
          "pf_legumes_totals",
          "pf_total_totals",
          #"pf_soy_totals_Binary",
          "v_drkgr_totals",
          "v_redor_total_totals",
          #"v_redor_tomato_totals",
          #"v_redor_other_totals",
          "v_starchy_total_totals",
          #"v_starchy_potato_totals",
          #"v_starchy_other_totals",
          "v_other_totals",
          "v_total_totals",
          #"v_legumes_total",
          "g_whole_totals",
          "g_refined_totals",
          "g_total_totals",
          "d_total_totals",
          "d_milk_totals",
          "d_cheese_totals",
          "d_yogurt_totals",
          "hei_asa24_totalscore",
          "hei_asa24_totalveg",
          "hei_asa24_sfat",
          "choln_tnfs",
          "age",
          "ethnicity" ,
          "bmi_final",
          "tmao",
          "choline",
          "betaine",
          "carnitine")
table_food.fq <- CreateTableOne(vars = vars,
                                    strata = "tmao_quantile",
                                    data = full[full$sex == "Female",],
                                    factorVars = factorVars)
table_food.fq

# TMAO table by age bin - males
table_food.mq <- CreateTableOne(vars = vars,
                                    strata = "tmao_quantile",
                                    data = full[full$sex == "Male",],
                                    factorVars = factorVars)
table_food.mq

# TMAO table by sex
table_food.allq <- CreateTableOne(vars = vars,
                                    strata = "tmao_quantile",
                                    data = full,
                                    factorVars = factorVars)
table_food.allq
```

```{r Save food quantile tables}
table_save.fq <- print(table_food.fq, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
write.csv(table_save.fq, file = "../../Outputs/tables/ParticipantChar/Food_Female_byTMAOQuantile.csv")

table_save.mq <- print(table_food.mq, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
write.csv(table_save.mq, file = "../../Outputs/tables/ParticipantChar/Food_Male_byTMAOQuantile.csv")

table_save.allq <- print(table_food.allq, quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
write.csv(table_save.allq, file = "../../Outputs/tables/ParticipantChar/Food_All_byTMAOQuantile.csv")
```

@@

```
```

"waistavg_cm", "sysbpavgv2", "diabpavgv2", "endo_rhi", "endo_al75", "hdl_bd1", "ldl_bd1", "chol_bd1", "tg_bd1_ln", "glc_bd1_ln","tnfa_bd1_ln", "il6_bd1_ln", "crp_bd1_ln",

BS section below...
```{r}
full$low_mps_meat <- ifelse(full$pf_mps_total_totals <= median(full$pf_mps_total_totals), "low", "high")
full$low_mps_meat <- ifelse(full$pf_mps_total_totals <= 9.091, "low", "high")
summary(lm(glc_bd1_ln ~  tmao_log + sex*age + cystatinc_bd1, full[full$low_mps_meat == "high",]))
summary(lm(glc_bd1_ln ~  tmao_log + sex*age + cystatinc_bd1, full[full$low_mps_meat == "high",]))
```

>>>>

1) Descriptive tables describing participants
2) Diet-TMAO analysis results
3) CVD-TMAO analysis results

@@

Create TMAO tertile descriptive table

@@

```{r save food linear regression table}
# Save table
write.csv(res_food, "../../Outputs/tables/Diet/MultipleLinReg_TMAO_LCMS_n356_ASA24.csv")
```

@@
